Asymmetric Agents and their Willingness to Fight\\ Customer Loyalty and its Impact on Competition

### 2015-09-28 Paper1.tex
illustration of changes

Consider the market for smartphones. Two firms compete over customers with heterogeneous preferences. For simplicity assume that devices are sold at an exogenously given price such that firm $1$ derives a profit of $\gamma_i$ from each customer.

Customer $k$ exhibit a preference for one of the two products that is given by $\theta_k$. $\theta_k\gg0$ implies that customers $k$ has a strong preference for the device sold by firm $2$, $\theta_k\ll0$ that she has a strong preference for product $1$ and $\theta_k\approxeq 0$ that she has a preference for neither of the firms. Preferences of the customers are distributed according to the cdf $G(\cdot)$ and the pdf $g(\cdot)$.

@@

Firms compete in R\&D efforts to increase the quality of their own products. While having a higher quality level helps to gain customers from the competitors, it does not help to increase the return per customer. People are willing to pay a certain amount for a smartphone, but as better products enter the market, the prices for the worse products decrease so that the quality frontier always receives the same valuation.

@@

If firm uses a superior technology than its competitor, only the customers highly loyal to firm $2$ will continue tu purchase its devices. Thus, the demand for firm $1$ is given by:
\begin{align*}
G(x_1-x_2)
\end{align*}

>>>>

look: I added a sentence here

Consider the market for smartphones. Two firms compete over customers with heterogeneous preferences. For simplicity assume that devices are sold at an exogenously given price such that firm $1$ derives a profit of $\gamma_1$ from each customer.

Customer $k$ exhibits a preference for one of the two products that is given by $\theta_k$. $\theta_k\gg0$ implies that customers $k$ has a strong preference for the device sold by firm $2$, $\theta_k\ll0$ that she has a strong preference for product $1$ and $\theta_k\approxeq 0$ that she has a preference for neither of the firms. Preferences of the customers are distributed according to the cdf $G(\cdot)$ and the pdf $g(\cdot)$.

@@

Firms compete in R\&D efforts to increase the quality of their own products. While having a higher quality level helps to gain customers from the competitors, it does not help to increase the return per customer. People are willing to pay a certain amount for a smartphone, but as better products enter the market, the prices for the worse products decrease so that the quality frontier always receives the same valuation. But if my product is $\gamma$ better than previous generation, my profits are likely to be $\gamma$ higher? Or is $\gamma$ not related to product quality?

@@

If firm uses a superior technology than its competitor, only the customers highly loyal to firm $2$ will continue to purchase its devices. Thus, the demand for firm $1$ is given by:
\begin{align*}
G(x_1-x_2)
\end{align*}
x is now quality?
